\documentclass{article}

\usepackage{verbatim}

% need tight spacing
\usepackage{parskip}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\usepackage[margin=22mm]{geometry}

% and nice fonts
\usepackage{bookman}
\usepackage[T1]{fontenc}
\usepackage[compact]{titlesec}


% for consistency in subsections
% usage: \position{title}{date}
\newcommand{\position}[2]{
  \textit{#1 (#2)}
}
% usage: \affiliation{institution}{location}
\newcommand{\affiliation}[2]{
  \textbf{#1}, #2 \\*
}
\usepackage{paralist}
\newenvironment{achievements}{
  \begin{compactitem} }{
  \end{compactitem}
}
\newcommand{\skill}[2]{
  \textbf{#1}: #2
  \smallskip
}

\newcommand{\skillNS}[2]{
  \textbf{#1}: #2
}

% usage: \hack{hackathon}{date}{description}
\newcommand{\hack}[3]{
  \textbf{#1} \textit{(#2)}: #3
  \smallskip
}

% header
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\setlength{\headheight}{50pt}
\fancyhead[C]{
  \textbf{\large Marcella Hastings} \\ 
  50 Curtis Avenue $\bullet$ Somerville, MA 02144\\
  marcellahastings@gmail.com \\
  952 $\bullet$ 688 $\bullet$ 2246}

\begin{document}
\subsection*{Education}
  \affiliation{Tufts University}                             {Medford, MA}
    \position{Bachelor of Science in Computer Science, Math} {May 2015} \\
  GPA 3.71, Dean's List 2011-2014 \\
  \skill{Relevant Coursework}
        {Programming Languages, Computational Biology, Machine Structure \&
        Assembly Level Programming, Cryptography, Real Analysis, Algorithms,
        Advanced Functional Programming Seminar, Computational Theory, 
        Computer Graphics}

\subsection*{Experience}
  \affiliation{MIT Lincoln Laboratory}       {Lexington, MA}
    \position {Summer Research Student}      {May 2014 - August 2014}
    \begin{achievements}
      \item Developed end-to-end prototype for a cryptographically secure
      mechanism to allow users to authenticate to services from a single
      fortified device.
    \end{achievements}
    \smallskip

  \affiliation{Google}                       {New York City, NY}
    \position {Engineering Practicum Intern} {May 2013 - August 2013}
    \begin{achievements}
      \item Worked with a partner and two mentors to develop a
            saving filters feature for the \\ DoubleClick for Publishers team.
      \item Created the client-facing interface for the feature and
      implemented saving functionality in Java.
    \end{achievements}
    \smallskip

  \affiliation{Tufts University}   {Medford, MA}
    \position {Teaching Assistant} {September 2012 - present}
    \begin{achievements}
      \item Taught hands-on programming labs to introductory CS students and
      held regular office hours for one-on-one assistance
      \item Lead TA training sessions and small-group meetings throughout the
      semester to promote motivation and consistency in the TA community
    \end{achievements}
    \smallskip

  \affiliation{Brain State Technologies}  {Bloomington, MN}
    \position {Intern, Software Division} {August 2012}
    \begin{achievements}
      \item Worked with a mentor to develop applications to assist in the
            retrieval, inspection, and update of XML based signal processing 
            flow designs.
      \begin{comment}
      \item Defined XML schema to bind application configuration parameters to 
            Java objects (using Apache XMLBeans).
      \end{comment}
    \end{achievements}

    \position {Intern/Senior Project, Software Divison} {May 2011}
    \begin{achievements}
      \item Worked with a small team to develop an up-sampling filter for a
      proprietary signal processing flow engine to align signal data from
      sources with varying sample rates.
    \end{achievements}

\subsection*{Hackathons}
  \textit{Source code is available on GitHub:
  \texttt{https://github.com/marsella}} \\
  \hack{HackingArts} {Sept 2013} 
        {Place different sounds around a circle to create musical loops that
        can be connected, harmonized, or turned into noisemakers. Wrote a web
        app called Looper to play with HTML5 Canvas and
        Javascript. \texttt{http://tinyurl.com/looperhack}} \\
  \hack{University Hacker Olympics} {Sept 2013} 
        {Need to find out who is the reigning office ping-pong champion?
        Upload your scores from the Balls of Fury app and check out
        the Elo rankings online to see how you stack up. Developed Android app 
        and logos.} \\ 
  \hack{PennApps} {Sept 2013} 
        {Tired of wrangling cloud storage? Nimbus stripes files
        across all of your storage accounts so you don't have to worry about
        distributing them. Created a unified interface for storage APIs.}

\begin{comment}
\subsection*{Projects}
  \skill{Type Inference}
        {Implemented Hindley-Milner type inference for a teaching language in
        ML. Wrote a constraint solver to assign types to correct terms and
        reject ill-typed terms.} \\
  \skill{TapItOut}
        {Developed the front end of a native Android app that allows
        peer-to-peer money transfer using NFC technology. Built at the 2013
        University Hacker Olympics in San Francisco.} \\
  \skill{Virtual Machine}
        {Designed and wrote a 32-bit virtual machine in C. Implemented a set of
        basic operations and a macro assembler to create executable binary
        files. Wrote a calculator program in assembly.}
\end{comment}

\subsection*{Skills}
  \skillNS{Languages} {C/C++, Java, Python, some Javascript,
                      Haskell, Scheme, Standard ML, XML, HTML/CSS}\\
  \skillNS{Tools}     {LaTeX, git, OS X, Unix/Linux, Eclipse, AutoCAD 2012}

\subsection*{Leadership}
\begin{minipage}[b]{0.5\linewidth}
Computer Science Exchange, \textit{president} \\
Tufts Hackathon, \textit{organizer}
\end{minipage}
\hspace{0.25cm}
\begin{minipage}[b]{0.5\linewidth}
Orthodox Christian Fellowship, \textit{president} \\
Tufts Jumbo Talk, \textit{blogger}
\end{minipage}

\end{document}

